Response to reviewers

### 2025-05-18 src/docs_paper-jtb/revisions.Rmd
Figure related edits

@@

>>>>

> Questions about the HIV model

Jeff broadly agrees with the reviewer.
(This is an area of current work on Naomi extension.)

> Selecting dimensions in proportion to variance in some outcome explained

@@

> On Figure 5

Thank you for the suggestion.
We have adjusted the `alpha` value from 0.5 to 0.1 and added a caption to the figure explaining the possible overlap to make the figure clearer.

```{r}
knitr::include_graphics("revisions/fig5_edit.png")
```

> On Figure 6

Thank you for noting that the $y$-axis here is ambiguous.
We have clarified this here and in other instances throughout the manuscript.
(Remains to do this!)

> On Figure 7

We agree that there are too many colours here for this figure to be clear.
Thank you for the good suggestion to split the plot into multiple panels.
We have done this, choosing to group the parameters by the component of the model they are most associated with.
(Remains to do this!)
